**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2020-12-10 paper/paper.Rmd

@@

@@

@@

>>>>

TODO: Describe OptiClust and vsearch.

@@

TODO: brief description of OptiFit algorithm. the method we came up with is the result. OptiClust paper had toy example to walk through the algorithm.

TODO: Paragraph at beginning to describe datasets: why picked, how processed

@@

TODO: compare optifit performance for split dataset vs public database
TODO: double-check with Sarah that MCCs are from full OTU dataset or just query sequnce OTUs
TODO: double-check reference fractions aren't flipped (fraction mapped plot looks weird)

@@

TODO: move this into first section with public database.
vsearch is more permissive than mothur (radius vs diameter with 0.03 dissimilarity threshold).
